%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\def\myauthor{Fangzhou Sun}
\def\mytitle{fsun-vita}
\def\myemail{fzsun@vt.edu}
\def\myphone{(540) 750-0370}
\def\myweb{sun.fangzhou.me}
\def\mykeywords{
  fangzhou sun,
  resume, 
  curriculum, 
  vita, 
  curriculum vita, 
  cv
}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage[
  pdftex,
  ocgcolorlinks,
  urlcolor={[rgb]{0,0,0.54}},
  unicode,
  plainpages=false,
  pdfpagelabels,
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfkeywords={\mykeywords}
]{hyperref}

\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{url}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright


% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\setlength{\tabcolsep}{0in}
\setlength{\parskip}{0em} % paragraph spacing
\linespread{1.1} % line spacing
\setlist[itemize]{leftmargin=\dimexpr 1em, noitemsep, topsep=0pt, after=\vspace{.2ex}} % itemize spacing
\renewcommand{\labelitemi}{-} 
\renewcommand{\labelitemii}{$\circ$} 

%-------------------------
% Pick a font: http://www.tug.dk/FontCatalogue/seriffonts.html
\usepackage[T1]{fontenc}
\usepackage{kpfonts}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l@{\extracolsep{\fill}}r}
\multirow{2}{*}{\huge \scshape \myauthor} & \small 1740 Donlee Dr., & \href{mailto:\myemail}{\small \myemail}\\
   & \small Blacksburg, VA 24060 & \href{tel:\myphone}{\small \myphone} 
\end{tabular*}
\vspace{-3ex}

%-----------Summary-----------------
\section{Summary}
\begin{itemize}
	\item 4+ years of experience on optimal control of manufacturing/logistics systems and revenue management.
	\item Over 5 hands-on projects in building optimization/simulation/statistics-based decision support tools. 
	\item Energetic self starter, outstanding analytical ability and strong communication skills.
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\textbf{Virginia Polytechnic Institute and State University (Virginia Tech)}, Blacksburg, VA \\ 

\begin{itemize}
	\item {Ph.D. in \href{https://www.ise.vt.edu/}{Operations Research}}  (GPA: 3.92/4.00)  \hfill{\textsc{Sep} 2018 (\textsc{expected})}
	
	 \begin{itemize}[after=]
		\item Advisor: \href{https://www.ise.vt.edu/People/Faculty/Bios/Sarin_bio.html}{Dr. Subhash C. Sarin}.
	\end{itemize}
	\item  {M.S. in Industrial and Systems Engineering}  (GPA: 3.90/4.00)\hfill {2016} 
\end{itemize}

\textbf{Tongji University,} Shanghai, China 
\begin{itemize}
	\item {B.E. in {Industrial Engineering}} (GPA: 4.64/5.00; Rank: 2/55)   \hfill{2013}  
\end{itemize}


%--------Computer SKILLS------------
\section{Computer Skills}
\begin{tabular*}{\textwidth}{l@{\extracolsep{1in}}l}
  \textbf{~~~Programming Languages:} C$++$, Python, VBA, C\#. &  \textbf{Database:} SQL, Access. \\
 \textbf{~~~Optimization:} CPLEX/OPL, AMPL. &  \textbf{Simulation:} AutoMod, ProModel, Simio. \\
 \textbf{~~~Scientific Computing:} R, Mathematica. & \textbf{Others:} Git, AutoCAD.
\end{tabular*}

%-----------Graduate Coursework-----------------
\section{Graduate Coursework}
\hangindent=1.5em \textbf{Operations Research:} Linear/Nonlinear/Integer/Dynamic Programming, Scheduling and Sequencing Theory, Random Processes, Simulation.
	
\hangindent=1.5em \textbf{Statistics \& Mathematics:} Probability Theory, Statistical Inference, Statistical Learning,  Real Analysis.

\hangindent=1.5em \textbf{Manufacturing \& Logistics:} Manufacturing Systems Engineering, Production Planning \& Control, Lean Manufacturing, Semiconductor Manufacturing, Inventory and Operations Management.

%-----------EXPERIENCE-----------------
\section{Related Experience}

    \textbf{PROS,} Houston, TX (a pricing and revenue management solution company)\\
\textbf{Scientist Intern (Optimization)} \hfill{\textsc{Jun 2017 -- Aug 2017}} 

\textit{Pareto Frontier in Revenue Management} \textsuperscript{[1]}
\begin{itemize}
	\item Proposed a constrained stochastic dynamic programming-based approach to generate Pareto frontier of conflicting airline objectives (expected revenue vs. load factor).
\end{itemize}

 
\textit{Airline Customer Value Study}
\begin{itemize}
	\item Built 15+ automation tools (Python and VBA) on analyzing past flight data to estimate customer potential revenue if switch to network-based products. 
	\item Optimized the code and reduced run time by 97\%, saving weeks of overall analysis time. 
%	\item The tools will be used for future value studies, and continue to benefit the company.
\end{itemize}

 
\textit{3-day Hackathon}
\begin{itemize}
	\item Proposed and developed an opportunity-based dynamic flight destination recommendation engine. 
	\item Predicted market opportunities using ridge regression with time series models.
\end{itemize}


\medskip
\textbf{Virginia Tech}, Blacksburg, VA  \\
\textbf{(Winner)}\textit{ IISE Student Case Competition in Logistics and Supply Chain}  \hfill{\textsc{Feb 2017 -- Mar 2017}}
\begin{itemize}
	\item Proposed a two-stage approach for the strategic network design and the operational decisions. 
	\item Proposed tight mathematical formulations and used decomposition to accelerate. Computational test revealed a reduction of the solution time by $10^3 +$ times.
	\item Coded a computer decision support tool based on our proposed approach (C$++$ with CPLEX). 
\end{itemize}

 
\textit{Biomass Feedstock Logistics}    \hfill{\textsc{Aug 2016 -- present}} 
\begin{itemize}
	\item Identified different integrated biomass feedstock supply chain problems with structural insights.
	\item Proposed a Dantzig-Wolfe decomposition framework for the integrated biomass feedstock supply chain problem.
	\item Formulated a fleet management model in the design of a switchgrass-based bio-ethanol supply chain.
\end{itemize}

%\newpage
 
\textit{Joint Supply Chain Operations} \textsuperscript{[3,4]}   \hfill{\textsc{Jun 2015 -- Jun 2017}} 
\begin{itemize}
	\item Identified the structure of the optimal shipping policy via a Lagrangian multiplier method for joint scheduling of a vendor-buyer system. Proposed a dynamic programming-based algorithm.
	\item Proposed solution methods (both exact and heuristic) for a joint production scheduling and shipping problem with a batching feature.
\end{itemize}

 

  
\textit{Semiconductor Fab Simulation} \hfill{\textsc{Aug 2014 -- Dec 2014}} 
\begin{itemize}
\item Built simulation models (using AutoMod) of the Automated Material Handling System (AMHS).
\item Proposed a coding framework for simulating complex AMHS, allowing flexibly adjusted process sequences.
\item Analyzed different scenarios (multiple releasing and dispatching rules) based on cycle time and throughput. 
\end{itemize}

  
\textit{Graduate Teaching Assistant} \hfill{\textsc{Aug 2014 -- May 2016}} 
\begin{itemize}
	\item Prepared and instructed 10+ different manufacturing and electrical labs.
	\item Presented workshops for graduate level students in using simulation softwares (AutoMod and AutoSched).
	\item Graded homework and exams, held office hours, and assisted other teaching tasks.
\end{itemize}



\medskip
\textbf{Volkswagen Automotive}, Shanghai, China  \\
\textbf{Logistics Intern} \hfill{Jul 2012 -- Aug 2012}
\begin{itemize}
  \item Inquired suppliers the delivery costs of purchased parts, and updated the information in database.
  \item Communicated with suppliers to implement a new Just-In-Time system.	
\end{itemize}



%-----------Publications-----------------
\section{Publications}
\hangindent=1.5em [1] \textbf{Fangzhou Sun,} Wei Wang, and Darius Walczak. \emph{On generating efficient frontier for expected profit contribution and resource utilization}. In preparation. 

\hangindent=1.5em [2] \textbf{Fangzhou Sun}, Rahul Ramachandran,  Maichel M. Aguayo, and Subhash C. Sarin. \emph{A taxonomic review of biomass feedstock supply chain problems}. In preparation, target: International Journal of Production Research.

\hangindent=1.5em [3] \textbf{Fangzhou Sun} and Subhash C. Sarin. \emph{A Joint Production and Delivery Schedule for a Single-Vendor Single-Buyer System over Finite Horizon}. In preparation, target: European Journal of Operational Research.
 
\hangindent=1.5em [4] \textbf{Fangzhou Sun,} Subhash C. Sarin, and Yuqiang Wang. \emph{Integrated production and shipping scheduling for a single manufacturer and multiple customers}. Submitted to Journal of Scheduling. 

%-----------Presentations-----------------
\section{Presentations}
\begin{itemize}
	\item \emph{Introduction to AutoMod and AutoSched AP}. Workshop, Virginia Tech. \hfill{2016}
	\item \emph{Integrated production and shipping scheduling for a single manufacturer and multiple customers}. \hfill{2015}
			\\ INFORMS Annual Meeting, Philadelphia, PA. 
\end{itemize}

%-----------Other Experience-----------------
\section{Other Experience}
\textbf{Vice President}, INFORMS VT Student Chapter \hfill{\textsc{Aug 2015 -- May 2016}}
\begin{itemize}
	\item Managed finance and memberships of the student organization. 
	\item Raised average weekly seminar attendance by 30\% more than the previous academic year.
	\item Won INFORMS 2016 Student Chapter Annual Award, Magna Cum Laude. 
\end{itemize}

%--------Awards and Honors------------
\section{Selected Awards and Honors}
First Place Award, IISE 2017 student case competition in Logistics and Supply Chain, \textit{IISE}.  \hfill{2017} \newline 
Graduate Student Assembly Travel Fund, \emph{Virginia Tech}. \hfill{2015} \newline 
Alpha Pi Mu, a national industrial engineering honor society, \textit{Virginia Tech}. \hfill{2014} \newline
Various awards including: Outstanding Graduate, 1st Prize Scholarship, etc., \emph{Tongji University}. \hfill{2010 -- 2013} \newline
Provincial 1st Prize, Chinese Physics Olympiad, \emph{Chinese Physics Society}. \hfill{2009
%-------------------------------------------

\end{document}
