\documentclass[11pt,letterpaper]{article}
% compile with xelatex
\def\myauthor{Fangzhou Sun}
\def\mytitle{fsun-vita}
\def\myemail{fzsun@vt.edu}
\def\myphone{(540) 750-0370}
\def\myweb{sun.fangzhou.me}
\def\mykeywords{
  fangzhou sun,
  resume, 
  curriculum, 
  vita, 
  curriculum vita, 
  cv
}

\setlength\parindent{0pt}

\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}}%
{\end{itemize}}

\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=0.15in}
\usepackage[log-declarations=false]{xparse}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[top=.5in,bottom=0.5in,right=.4in,left=1.4in]{geometry}
\usepackage[strict]{changepage}
\usepackage[
  ocgcolorlinks,
  urlcolor={[rgb]{0,0,0.54}},
  unicode,
  plainpages=false,
  pdfpagelabels,
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfkeywords={\mykeywords}
]{hyperref}

% fix ocgcolor link breaking; thanks due to Benjamin Lerner (http://goo.gl/VZKR7M)
\makeatletter
\AtBeginDocument{%
  \newlength{\temp@x}%
  \newlength{\temp@y}%
  \newlength{\temp@w}%
  \newlength{\temp@h}%
  \def\my@coords#1#2#3#4{%
    \setlength{\temp@x}{#1}%
    \setlength{\temp@y}{#2}%
    \setlength{\temp@w}{#3}%
    \setlength{\temp@h}{#4}%
    \adjustlengths{}%
    \my@pdfliteral{\strip@pt\temp@x\space\strip@pt\temp@y\space\strip@pt\temp@w\space\strip@pt\temp@h\space re}}%
  \ifpdf
    \typeout{In PDF mode}%
    \def\my@pdfliteral#1{\pdfliteral page{#1}}% I don't know why % this command...
    \def\adjustlengths{}%
  \fi
  \ifxetex
    \def\my@pdfliteral #1{\special{pdf: literal direct #1}}% isn't equivalent to this one
    \def\adjustlengths{\setlength{\temp@h}{-\temp@h}\addtolength{\temp@y}{1in}\addtolength{\temp@x}{-1in}}%
  \fi%
  \def\Hy@colorlink#1{%
    \begingroup
      \ifHy@ocgcolorlinks
        \def\Hy@ocgcolor{#1}%
        \my@pdfliteral{q}%
        \my@pdfliteral{7 Tr}% Set text mode to clipping-only
      \else
        \HyColor@UseColor#1%
      \fi
  }%
  \def\Hy@endcolorlink{%
    \ifHy@ocgcolorlinks%
      \my@pdfliteral{/OC/OCPrint BDC}%
      \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
      \my@pdfliteral{F}% Fill clipping path (the url's text) with current color
      \my@pdfliteral{EMC/OC/OCView BDC}%
      \begingroup%
        \expandafter\HyColor@UseColor\Hy@ocgcolor%
        \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
        \my@pdfliteral{F}% Fill clipping path (the url's text) with \Hy@ocgcolor
      \endgroup%
      \my@pdfliteral{EMC}%
      \my@pdfliteral{0 Tr}% Reset text to normal mode
      \my@pdfliteral{Q}%
    \fi
    \endgroup
  }%
}
\makeatother
% end fixes


\newcommand{\mhead}[1]{\leavevmode\marginpar{\sffamily #1}}
\newcommand{\rdate}[1]{{\addfontfeature{Numbers=OldStyle} \hfill #1}}
\renewcommand{\date}[1]{{\addfontfeature{Numbers=OldStyle} #1}}
\renewcommand{\labelitemi}{-} 

\setmainfont[
  Ligatures={TeX,Common},
  BoldFont={AGaramondPro-Semibold},
]{Adobe Garamond Pro}
\setsansfont[
  Ligatures={TeX,Common},
  Letters=SmallCaps,
  Color=660000,
]{Adobe Garamond Pro}
\setmonofont{FontAwesome}

\pagestyle{fancy} 
	\setlength\headwidth{7.7in} 
	\lhead{\textsc{Fangzhou Sun}}
	\rhead{\textsc{\thepage{} of \pageref*{LastPage}}} \cfoot{}
	\thispagestyle{empty}

\begin{document} \flushbottom \thispagestyle{empty} \setlength\headheight{0in} 
\begin{adjustwidth}{-1in}{}
{\Huge
  {\textsc{%
    {\addfontfeature{Style=TitlingCaps}F}angzhou 
    %({\addfontfeature{Style=TitlingCaps}L}eo)
    {\addfontfeature{Style=TitlingCaps}S}un}
  }
}
\hfill\hfill\hfill
{
  \begin{minipage}[b]{1.7in}
    \flushleft \footnotesize 
    1740 Donlee Dr., \\
    Blacksburg, VA 24060
  \end{minipage}
  \hfill
  \begin{minipage}[b]{1.6in}
    \flushright \footnotesize 
    \href{mailto:\myemail}{\myemail} \\
    \href{tel:\myphone}{\myphone} \\
    \href{http://sun.fangzhou.me}{\myweb} %\href{http://www.linkedin.com/in/fangzhousun}{\texttt{}}\quad ~ 
  \end{minipage}
}\par
\hrulefill
\end{adjustwidth}  
\reversemarginpar 
\setlength\marginparwidth{.85in}

%-----------------Objective-------------------------------
%\mhead{Objective}%
%Seeking full time opportunities in areas of optimization, forecasting, data analytics, with applications in revenue management and control of production/logistics/supply chain systems. 

%\bigskip

%-----------------Summary-------------------------------
\mhead{Summary}%
- 6$+$ years of experience in IE/OR; 3$+$ years of experience in data science; 7$+$ years of experience in programming.  \\
- Over 5 hands-on project experiences in building optimization/simulation-based decision support tools. \\
- Energetic self starter, outstanding analytical ability and strong communication skills.

\bigskip
%---------------------Education---------------------------
\mhead{Education}%
\textbf{Virginia Polytechnic Institute and State University (Virginia Tech)}, Blacksburg, VA  

\hangindent=1em - {Ph.D. in \href{https://www.ise.vt.edu/}{Operations Research}}  (GPA: 3.92/4.00) \rdate{\textsc{Summer} 2018 (\textsc{expected})} \\
 $\circ$ Advisor: \href{https://www.ise.vt.edu/People/Faculty/Bios/Sarin_bio.html}{Dr. Subhash C. Sarin}. 

\hangindent=1em - {M.S. in Industrial and Systems Engineering}  (GPA: 3.90/4.00)\rdate{2016} 

\medskip
\textbf{Tongji University,} Shanghai, China 

\hangindent=1em - {B.E. in {Industrial Engineering}} (GPA: 4.64/5.00; Rank: 2/55)   \rdate{2013}  \\
	$\circ$ Thesis: {Scheduling of parallel machines with group maintenance considerations.}

\bigskip
%-----------------Computer Skills-----------------------------
 \mhead{Computer Skills}% 
~\\[-.8em] 
  \begin{minipage}[b]{3 in}
    \textbf{Programming Languages:} C$++$, C\#, VBA. \\
    \textbf{Optimization:} CPLEX/OPL, AMPL. \\
    \textbf{Scientific Computing:} R, Mathematica.
  \end{minipage}
  \hfill
  \begin{minipage}[b]{3 in}
    \textbf{Database:} SQL, Access. \\
    \textbf{Simulation:} AutoMod, ProModel, Simio.\\
    \textbf{Others:} AutoCAD.
  \end{minipage}
  \hfill


\bigskip
%--------------------Graduate Coursework----------------------------
\mhead{Graduate \newline Coursework}%
\hangindent=1em \textbf{Operations Research:} Linear/Nonlinear/Integer/Dynamic Programming, Scheduling and Sequencing Theory, Random Processes, Simulation.
	
\smallskip
\hangindent=1em \textbf{Statistics \& Mathematics:} Probability Theory, Statistical Inference, Machine Learning,  Real Analysis.

\smallskip
\hangindent=1em \textbf{Manufacturing \& Logistics:} Manufacturing Systems Engineering, Production Planning \& Control, Lean Manufacturing, Semiconductor Manufacturing, Inventory and Operations Management.
	




\bigskip
%-----------------------Related Experience-------------------------

\mhead{Related \newline Experience}%
%\textbf{Intern - Science and Research}, \textit{PROS,} Houston, TX \rdate{\textsc{Summer} 2017} 
%\begin{itemize*}
%	\item Proposed an iterative two-stage approach for the strategic network design and the operational decisions. 
%	\item Refined the original IP formulation, which resulted in a more compact and tighter model. Computational test revealed a reduction of the solution time by $10^3 +$ times.
%\end{itemize*}
%
%\medskip
%
\textbf{Virginia Tech}, Blacksburg, VA  \\
\textbf{(Winner)}\textit{ IISE Student Case Competition in Logistics and Supply Chain}  \rdate{\textsc{Feb 2017 -- Mar 2017}}
\begin{itemize*}
	\item Proposed an iterative two-stage approach for the strategic network design and the operational decisions. 
	\item Refined the original IP formulation, which resulted in a more compact and tighter model. Computational test revealed a reduction of the solution time by $10^3 +$ times.
	\item Coded a computer decision support tool based on our proposed approach (C$++$ with CPLEX). 
	\item Visualized our solution by the multidimensional scaling technique.
\end{itemize*}

\medskip
\textit{Biomass Feedstock Logistics}    \rdate{\textsc{Aug 2016 -- present}} 
\begin{itemize*}
	\item Identified different integrated biomass feedstock supply chain problems with structural insights.
	\item Proposed a Dantzig-Wolfe decomposition framework for the integrated biomass feedstock supply chain problem.
	\item Formulated a fleet management model in the design of a switchgrass-based bio-ethanol supply chain.
\end{itemize*}

\medskip
\textit{Joint Supply Chain Operations}   \rdate{\textsc{Jun 2015 -- present}} 
\begin{itemize*}
	\item Proposed structural properties and solution methods (branch-and-bound and dynamic programming) for a joint production scheduling and shipping problem with a batching feature.
	\item Identified the structure of the optimal shipping policy via a Lagrangian multiplier method for a joint production and shipping schedule of a vendor-buyer system. Proposed a dynamic programming-based algorithm.
\end{itemize*}

\medskip 
\textit{Semiconductor Fab Simulation} \rdate{\textsc{Aug 2014 -- Dec 2014}} 
\begin{itemize*}
\item Built simulation models (using AutoMod) of the Automated Material Handling System (AMHS).
\item Proposed a coding framework for simulating complex AMHS, which allows flexible and ease of adjustment of process sequences of lots.
\item Implemented and analyzed different scenarios (such as releasing and dispatching rules) for the best scenario based on cycle time and throughput. Identified the potential bottleneck of the AMHS.
\end{itemize*}

\medskip
\textit{Graduate Teaching Assistant} \rdate{\textsc{Aug 2014 -- May 2016}} 
\begin{itemize*}
	\item Prepared and instructed more than 10 different manufacturing and electrical labs.
	\item Presented workshops for graduate level students in using simulation softwares (AutoMod and AutoSched).
	\item Graded homeworks and exams, held office hours, and assisted other teaching tasks.
\end{itemize*}

\newpage \setlength\headheight{.5in}  

\textbf{Volkswagen Automotive}, Shanghai, China \\
\textit{Logistics Intern}    \rdate{Jul 2012 -- Aug 2012}
\begin{itemize*}
  \item Inquired suppliers the delivery costs of purchased parts, and updated the information in database.
  \item Communicated with suppliers to implement a new Just-In-Time system.	
\end{itemize*}



 


\bigskip
%-----------------Publications-------------------------------
\mhead{Publications}%
\hangindent=1em \textbf{Fangzhou Sun,} Subhash C. Sarin, and Yuqiang Wang. \emph{Integrated production and shipping scheduling for a single manufacturer and multiple customers}. Submitted to Omega. 

\smallskip
\hangindent=1em \textbf{Fangzhou Sun} and Subhash C. Sarin. \emph{A Joint Production and Delivery Schedule for a Single-Vendor-Single-Buyer System over Finite Horizon}. In preparation, target: European Journal of Operational Research. 

\smallskip
\hangindent=1em \textbf{Fangzhou Sun}, Rahul Ramachandran,  Maichel M. Aguayo, and Subhash C. Sarin. \emph{A taxonomic review of biomass feedstock supply chain problems}. In preparation, target: International Journal of Production Research.



\bigskip
%-----------------Presentations-------------------------------
\mhead{Presentations}%
%\emph{Conference paper}\\
\par\vspace{-\baselineskip}

\begin{itemize}
	\item \emph{Introduction to AutoMod and AutoSched AP}. Workshop, Virginia Tech. \rdate{2016}
	\item \emph{Integrated production and shipping scheduling for a single manufacturer and multiple customers}. \rdate{2015}
			\\ INFORMS Annual Meeting, Philadelphia, PA. 
\end{itemize}









\bigskip
%-----------------Other Experiences-------------------------------
\mhead{Other \newline Experience}%
\textbf{Vice President}, INFORMS VT Student Chapter \rdate{\textsc{Aug 2015 -- May 2016}}
\begin{itemize*}
	\item Managed finance and memberships of the student organization. 
	\item Raised the average weekly seminar attendance by 30\% more than the previous academic year.
	\item Won INFORMS 2016 Student Chapter Annual Award, Magna Cum Laude. 
\end{itemize*}

%\medskip
%
%\textbf{Variation Analysis for Wafer Data Using Regression and Kriging Methods}  \rdate{\textsc{Fall} 2013} 
%\begin{itemize*}
%\item Built a linear regression model to predict wafer thickness. Performed the variable selection by using BIC. 
%\item Used Kriging method to model the wafer data. Compared the performance of Kriging and linear regression.
%\end{itemize*}
%
%\medskip
%\textbf{Music Management System Design} \rdate{\textsc{Spring} 2012} 
%\begin{itemize*}
%\item Designed the database structure. Coded the interface and the internal logic by C\# and MS SQL Server.
%\end{itemize*}




\bigskip
%-----------------Honors & Awards-------------------------------
\mhead{Selected \newline Awards \& \\ Honors}%
First Place Award, IISE 2017 student case competition in Logistics and Supply Chain, \textit{IISE}.  \rdate{2017} \newline 
Graduate Student Assembly Travel Fund, \emph{Virginia Tech}. \rdate{2015} \newline 
Alpha Pi Mu, a national industrial engineering honor society, \textit{Virginia Tech}. \rdate{2014} \newline
Various awards including: Outstanding Graduate, 1st Prize Scholarship, etc., \emph{Tongji University}. \rdate{2010 -- 2013} \newline
Provincial 1st Prize, Chinese Physics Olympiad, \emph{Chinese Physics Society}. \rdate{2009}
%(only top 45 awarded in Sichuan province)




\end{document}